\Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}

### 2017-08-29 Manuscript.tex
Modified manuscript, included anova and tukeys HSD

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{\normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

Juan Carlos Villaseñor-Derbez\textsuperscript{1}

@@

\textbf{Full postal address}\\
Bren Hall\\
University of California at Santa Barbara\\
Santa Barbara\\
CA, 93106

\textbf{Corresponding author information:}\\
Juan Carlos Villaseñor-Derbez\\
Bren Hall\\
University of California at Santa Barbara\\
Santa Barbara\\
CA, 93106
\href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}
+1 207 205 8435

\textbf{Running title}\\
Allometric growth of Pterois volitans

@@

\textbf{Title of contribution}: Biometry of the invasive lionfish
(\emph{Pterois volitans}) in the Central Mexican Caribbean, and a review
of allometric growth parameters across the invasion range

\textbf{Abstract}\\
Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
North-Western Atlantic and the Caribbean, likely introduced through
liberation of aquarium-kept organisms. Due to its threat to local
biodiversity, the speed of their spread, and its difficulty of
management, their presence in these waters has been labeled as a major
marine invasion. In order to better manage the invasion, inform lionfish
removal programs, predict their possible impacts, and estimate biomass
available for harvest, we must be able to accurately estimate their
total biomass. This study reports allometric growth parameters
(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
central portion of the Mexican Caribbean. It also identifies that, for a
given length, organisms from the Caribbean tend to have lower weights
than those from the Gulf of Mexicoand Atlantic, indicating that
weight-at-length is spacialy variable. In addition to the new pair of
parameters provided in this study, other 13 pairs of allometric growth
parameters were used to calculate expected biomass from total length
observations. Mean expected-to-observed biomass ratios by study ranged
between 0.98 and 1.75, with overall values ranging from 0.44 to 3.51.
The large differences between observed and expected biomass when using
parameters from other locations highlights the importance of using
site-specific parameters to estimate biomass from length observations.
This becomes increasingly important when estimating biomass available
for harvest or effectiveness of lionfish removal efforts. Additionally,
guidelines on reporting allometric parameters are provided as a
suggestion for future research are provided.

@@

\textbf{Resumen}\\
Los peces león (\emph{Pterois volitans/miles}) son una especiei nvasora
en el Atlántico Noroeste y el Caribe, probablemente introducidos por
medio de la liberación de organismos de ornato. Dada la amenaza que
estos representan para la biodiversidad local, la velocidad de su
invasión y dificultad de manejo, su presencia ha sido catalogada como
una importante invasión marina. Para manejar mejor la invasión, proveer
información a los programas de remoción, predecir los posibles impactos
y estimar biomasa disponible para la extracción, debemos ser capaces de
estimar su biomasa con precisión. Este estudio presenta parámetros de
crecimiento alométrico (\(a = 3.2056\times 10^{-6}; b = 3.235\)) para
organismos muestreados en la porción central del Caribe Mexicano.
También identifica que para una misma longitud, los organismos del
Caribe tienden a ser menos pesados que aquellos del Golfo de México y
Atlántico, indicando variaciones espaciales en la relación
peso-longitud. Además de los parámetros descritos en este estudio, se
utilizaron otros 13 pares de parámetros de crecimiento alométrico para
estimar biomasa a partir de observaciones de talla. La razón entre
biomasa observada y biomasa esperada varió, en promedio por estudio,
entre 0.98 y 1.75, con valores extremos de 0.44 y 3.51. Las grandes
diferencias entre biomasa observada y esperada al usar parámetros de
otras regiones resalta la importancia de utilizar parámetros específicos
a la zona para estimar biomasa a partir de observaciones de talla.
Adicionalmente, se proveen sugerencias para estandarizar la manera en
que los parámetros de crecimiento alométrico se reportan.

\textbf{Palabras clave} pez león, Pterois volitans, relación
longitud-peso, crecimiento alométrico, México

@@

\section{Introduction}\label{introduction}

@@

\section{Materials and Methods}\label{materials-and-methods}

\subsection{Area of study}\label{area-of-study}

The study took place off the coasts of Playa del Carmen, in the Mexican
Caribbean (\textbf{Fig. 1}). The region represents the northernmost
section of the Mesoamerican Barrier Reef System (Ruiz-Zarate \&
Arias-Gonzalez, 2004). Coral reefs and mangroves are locally important
habitats that represent important sources of income in terms of
extractive (\emph{e.g.} recreational fishing) and non-extractive
(\emph{e.g.} SCUBA diving) activities related to tourism, the main
source of income to the local economy (Murray, 2007).

In the region, the reef profile has been described by Arias-Gonzalez
(1998), indicating that the reef lagoon extends about 500 m from the
coast, until the reef crest is reached. The reef becomes deeper, leading
to the reef front often found at 700 m from the coastline end extends
for an additional 300 m. At approximately 1000 m away from shore and 30
- 40 m depth, the reef leads to a drop-off. Along a perpendicular
profile to the coast, bands of reef are interrupted by sand patches at 8
- 12 m deep and 16-18 m deep. Along the coast, these reefs have been
reported to be under significant anthropogenic pressure, likely causing
a shift in structure and function (Bozec et al., 2008).

\subsection{Fish sampling}\label{fish-sampling}

Organisms sampled by Villaseñor-Derbez \& Herrera-P\a'erez (2014) for
stomach content analysis between May and August of 2010 were used in
this work. A total of 33 SCUBA immersions were performed in 10 sampling
sites along the coast (Fig. 1, Table 1). Sampling locations included
wall and carpet reefs at depths between 5.7 m and 38.1 m. All observed
organisms (n = 109) were collected using hand nets and numbered
collection bottles. The use of hand nets prevents any weight loss due to
bleeding(when collected with spears), and increases the range of sizes
that can be sampled, providing a representative sample of the
population. Information on depth and other comments were recorded in an
underwater slide. Depth was recorded by dive gauges held by divers as
safety procedures during the collections. Samples were frozen within 30
minutes of completing the dive and stored for posterior analysis in the
lab. For every organism Total Length (TL; mm) and Total Weight (TW; gr)
were recorded in the lab.

\subsection{Data analysis}\label{data-analysis}

The weight at length relationship between the observed variables is
described by the allometric growth function:

\begin{equation}TW = aTL^b\end{equation}

Where \(TW\) is the Total Weight (gr), \(TL\) is the observed Total
Length (mm), \(a\) is the ponderal index and \(b\) is the scaling
exponent or allometric parameter. When \(b = 3\), it is said that the
organism exhibits a perfect isometric growth. The dependent and
independent variables were transformed via base-10 logarithms so that
the equation is then:

\begin{equation}log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\end{equation}

To simplify this equation, we can re-write it as:

\begin{equation}Y = mX + c\end{equation}

Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
\(c = log_{10}(a)\). Since \(b == m\), we will only use \(b\) throughout
the paper for simplicity. The coefficients (\(c\) and \(b\)) were
estimated with an Ordinary Least Square Regression and
heteroskedastic-robust standard errors. Both coefficients were tested
against the null hypothesis of no change (\emph{i.e.} \(H_0: c = 0\) and
\(H_0: b = 0\)). Additionally, the allometric parameter was tested
against the null hypothesis of isometric growth (\(H_0: b = 3\)).
Coefficients were tested with a two-tailed Student's t-test. The
significance of the regression was corroborated with an F-test.

Other allometric growth parameters were obtained from peer-reviewed
literature. Parameters were obtained forNorth Carolina (Barbour et al.,
2011), Northern (Fogg et al., 2013) and Southern Gulf of Mexico
(Aguilar-Perera \& Quijano-Puerto, 2016), the Southern Mexican Caribbean
(Sabido-Itza et al., 2016), Little Cayman (Edwards, Frazer \& Jacoby,
2014), Jamaica (Chin, Aiken \& Buddo, 2016), Bonaire (de Leon et al.,
2013) and Costa Rica (Sandel et al., 2015). Additionally, parameters
from Fishbase (Froese \& Pauly, 2016) were also included in this study.
When available, information on sampling methods, gender differentiation,
location, and depth ranges of each study was retrieved. Whenever gender
was not specified, it was assumed that the results were presented for
both genders pooled together. During the review process, it was noticed
that some papers indistinctly use \(a\) to report either the ponderal
index in eq. 1 or the y-intercept (\(c\)) in eq. 3, which might
sometimes be overlooked. Furthermore, some studies report their
parameters as mm-to-gr conversions, but a rapid evaluation of such
parameters indicates that they were estimated as cm-to-gr conversions.
Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
required, values from other studies are transformed for consistency.

Since standard errors or confidence intervals were not provided for many
studies, it was impossible to test for statistical differences across
studies. Thus expected biomass for each organism was calculated with the
growth parameters estimated in this study, as well as those retrieved
from additional literature. All expected biomass values were divided by
the observed biomass to obtain a ratio that allowed rapid identification
of over- or underestimation with respect to the observed biomass.
Therefore, values lower than 1 indicate that the parameters
underestimate biomass, and values larger than 1 indicate overestimation.
Median and mean expected to observed biomass ratios were calculated for
each study.

All hypothesis testing was performed with a confidence level of
\(\alpha = 0.01\) in R version 3.4.0 (R Core Team, 2017). Data wrangling
was performed with the tidyverse package (Wickham, 2017). Maps were
created with a mix of functions from the sp (Pebesma \& Bivand, 2005),
rgdal (Bivand, Keitt \& Rowlingson, 2017), tmap (Tennekes, 2017a), and
tmaptools (Tennekes, 2017b) packages. Calculation of
heteroskedastic-robust standard errors was done with the sandwich
(Zeileis, 2004) and lmtest (Zeileis \& Hothorn, 2002) packages. Models
were manipulated with with the broom package (Robinson, 2017). Stargazer
(Hlavac, 2015), knitr (Xie, 2017), and kableExtra (Zhu, 2017) were used
to produce the tables, and RefManageR (McLean, 2014) was used to keep
track of citations. The manuscript was written in r markdown (Allaire et
al., 2017) and processed with the knitr package (Xie, 2017). Raw data
and code used in this work is available at
\url{github.com/jcvdav/lionfish_biometry}.

\section{Results}\label{results}

Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7
gr. The smallest organism (TL = 34.00 mm) was also the lightest organism
(TW = 0.30 gr). However, the largest organism (TL = 310.00 mm) was not
the heaviest (TW = 303.70 gr), and the heaviest organism (TW = 397.70
gr) was 292.00 mm in total length. Kernell density plots (Fig. 2) show
the distribution for TL and TW. Both measures were positively skewed,
with skewness of 0.85 for TL and 2.19 for TW.

\subsection{Length-weight
relationship}\label{length-weight-relationship}

The model adjusted to eq. 3 estimated the coefficient values at
\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
calculated from TL (mm) as a linear equation:
\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\) or its
exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
The intercept (\(c\)) and slope \((b)\) were significantly different
from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
respectively), rejecting the null hypothesis of no change. Additionally,
the allometric factor (\(m = b\)) was significantly different from the
value of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)),
indicating that lionfish present allometric growth. More information on
model fit and confidence intervals for the estimated coefficients is
presented in Table 2. The relationship between Total Length and Total
Weight is presented in Figure 3.

\subsection{Comparison of allometric
parameters}\label{comparison-of-allometric-parameters}

From the eight peer-reviewed studies including information on growth
parameters for \emph{P. volitans} and Fishbase (Froese \& Pauly, 2016),
13 parameters were identified (Table 3). Two studies (Fogg et al., 2013;
Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and pooled
parameters, while the rest of the studies always presented pooled
results. The smallest coefficient of determination was presented by
Chin, Aiken \& Buddo (2016) with \(R^2 = 0.8715\), while Sabido-Itza et
al. (2016) reported the highest value at \(R^2 = 0.9907\). These studies
presented information for organisms obtained at depths between 0.5 and
57 m. Two studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken
\& Buddo, 2016) explicitly stated that their organisms were sampled with
pole spears. Five studies (Barbour et al., 2011; Fogg et al., 2013;
Edwards, Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et
al., 2016) mentioned that some of their organisms were obtained with
pole spears (or other type of harpoon). A single study (de Leon et al.,
2013) did not specify how samples were obtained.

Parameters from models fit to males or females exclusively tend to have
a higher steepness (\emph{i.e.} higher allometric parameter), with mean
\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
\(b = 3.31 \pm 0.23\) males and females respectively, compared to
parameters from models for pooled genders with a mean \(\pm\) standard
deviation value of \(b = 3.09 \pm 0.22\). In the case of the ponderal
index (\(a\)) and its \(log_{10}\) transformed parameter (\(c\)), values
were higher for parameters for pooled genders. Figure 4 shows the
predicted weights for organisms within the size range of these study
using the 14 parameters previously described.

From all allometric parameters reviewed, those of Edwards, Frazer \&
Jacoby (2014) slightly underestimated the observed biomass, with median
(0.96) and mean (0.98) bellow one. There is no significance in comparing
the parameters estimated in this study since, by definition, they are
the pair of parameters for which residual sum of squares was minimized
with values of median =1.00 and mean =1.03. For all the other studies,
the 95\% confidence interval around the mean fell further away from a
value of 1, indicating overestimation. Predicted to observed biomass
ratios are presented in Figure 5.

\section{Discussion}\label{discussion}

This study provides the first pair of allometric growth parameters
specific to the Central Mexican Caribbean, complementing other studies
performed in Mexican waters in the Alacranes Reef (Aguilar-Perera \&
Quijano-Puerto, 2016) and Xcalak National Park (Sabido-Itza et al.,
2016). By using hand nets instead of spears, we are able to sample a
wider range of sizes often ignored by pole spear samples, allowing us to
include smaller organisms. Estimating parameters by including smaller
organisms ensures better estimatio of weight for smaller sizes. This is
especially important when biomass is calculated from visual census,
where small organisms can be registered. Thus, this study is the first
to provide allometric growth parameters for lionfish in the central
region of the Mexican Caribbean and increases certainty in weight
estimation of small organisms.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{\Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{\textbf{Running title}: Allometric growth of Pterois volitans}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

Juan Carlos VILLASEÑOR-DERBEZ\textsuperscript{1}

@@

* Correspondence: Juan Carlos Villaseñor-Derbez, Bren Hall, University
of California at Santa Barbara, Santa Barbara, CA, 93106, US phone: +1
207 205 8435, e-mail:
\href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}

@@

\textbf{Background.} Lionfish (\emph{Pterois volitans/miles}) are an
invasive species in the North-Western Atlantic and the Caribbean. In
order to better manage the invasion, inform lionfish removal programs,
predict their possible impacts, and estimate biomass available for
harvest, we must be able to accurately estimate their total biomass.
Previous work has identified that lionfish age-at-length relationships
are spatially variable across the invasion range. This work had two main
objectives: i) compare length-weight relationships of the invasive
lionfish through the invasion range; and ii) Report the length-weight
frequency for lionfish in the Central Meixcan Caribbean.

\textbf{Materials and methods.} A total of 13 length-weight
relationships reported in eight peer-reviewed studies and FishBase were
used to calculate expected biomass of organisms (n = 109) sampled from
the Central Mexican Caribbean, whose Total Length (TL) and Total Weight
(TW) were known. For each length-weight relationship,
expected-to-observed weight ratio was calculated for each organism.
Differences in mean expected-to-observed weight ratios were tested with
a one-way ANOVA; Tukey's HSD was used as a post-hoc test to identify
groups of non-statistically significant differences. Additionally, the
length-weight relationship of the 109 organisms was calculated. Total
Length (TL) and Total weight (TW) were log10-transformed to fit a linear
model describing the linearized length-weight relationship. The model
was fit using Ordinary Least Squares and Heteroskedastik-robust standard
errors were computed.

\textbf{Results.} Expected-to-observed weight ratios ranged from 0.44 to
3.51, and dfferences in weight-at-length were spatially consistent. For
a given length, parameters from the Caribbean yielded lower weights than
those from the Gulf of Mexico and Atlantic, indicating that
weight-at-length is spatially variable. This study also reports a new
pair of length-weight parameters
(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
Central Mexican Caribbean.

\textbf{Conclusion.} The large differences between observed and expected
biomass when using parameters from other locations highlights the
importance of using site-specific parameters to estimate biomass from
length observations. Findings from this work can aid managers and
decision makers to better select length-weight parameters when these are
not available for their region of interest.

@@

@@

\section{INTRODUCTION}\label{introduction}

@@

\section{MATERIALS AND METHODS}\label{materials-and-methods}

\textbf{Area of study.} The study took place off the coasts of Playa del
Carmen, in the Mexican Caribbean (\textbf{Fig. 1}). The region
represents the northernmost section of the Mesoamerican Barrier Reef
System (Ruiz-Zarate \& Arias-Gonzalez, 2004). Coral reefs and mangroves
are locally important habitats that represent important sources of
income in terms of extractive (\emph{e.g.} recreational fishing) and
non-extractive (\emph{e.g.} SCUBA diving) activities related to tourism,
the main source of income to the local economy (Murray, 2007).

The reef profile has been described by Arias-Gonzalez (1998), indicating
that the reef lagoon extends about 500 m from the coast, until the reef
crest is reached. The reef becomes deeper, leading to the reef front
often found at 700 m from the coastline and extends for an additional
300 m. At approximately 1000 m away from shore and 30 - 40 m depth, the
reef leads to a drop-off. Along a perpendicular profile to the coast,
bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18
m deep. Along the coast, these reefs have been reported to be under
significant anthropogenic pressure, likely causing a shift in structure
and function (Bozec et al., 2008).

\textbf{Fish sampling.} A total of 33 SCUBA immersions were performed in
10 sampling sites along the coast in 2010 (Fig. 1, Table 1). Sampling
locations included wall and carpet reefs at depths between 5.7 m and
38.1 m. All observed organisms (n = 109) were collected using hand nets
and numbered collection bottles. The use of hand nets prevented any
weight loss due to bleeding and allowed a better representation of small
sizes, often ignored due to gear selectivity when spearing. Organisms
were euthanized and frozen within 30 minutes of completing the dive and
stored for posterior analysis. Total Length (TL; mm) and Total Weight
(TW; gr) were recorded for all organisms.

\textbf{Data analysis.} The weight at length relationship between the
observed variables is described by the allometric growth function:

\[TW = aTL^b\]

Where \(TW\) is the Total Weight (gr), \(TL\) is the Total Length (mm),
\(a\) is the ponderal index and \(b\) is the scaling exponent or
allometric parameter. When \(b = 3\), it is said that the organism
exhibits a perfect isometric growth. The dependent and independent
variables were transformed via base-10 logarithms, thus the equation
becomes:

\[log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\]

This can be simplified and re-written as:

\[Y = mX + c\]

Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
\(c = log_{10}(a)\). Since \(b = m\), we will only use \(b\) throughout
the paper for simplicity. The coefficients (\(c\) and \(b\)) were
estimated with an Ordinary Least Square Regression and
heteroskedastic-robust standard error correction was performed. Both
coefficients were tested against the null hypothesis of no change
(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)). Additionally, the
allometric parameter was tested against the null hypothesis of isometric
growth (\(H_0: b = 3\)). Coefficients were tested with a two-tailed
Student's t-test. The significance of the regression was corroborated
with an F-test.

Other length-weight relationships (n = 13) were extracted from
peer-reviewed literature. Parameters were obtained for North Carolina (n
= 1; Barbour et al., 2011), Northern (n = 3; Fogg et al., 2013) and
Southern Gulf of Mexico (n = 3; Aguilar-Perera \& Quijano-Puerto, 2016),
the Southern Mexican Caribbean (n = 1; Sabido-Itza et al., 2016), Little
Cayman (n = 1; Edwards, Frazer \& Jacoby, 2014), Jamaica (n = 1; Chin,
Aiken \& Buddo, 2016), Bonaire (n = 1; de Leon et al., 2013) and Costa
Rica (n = 1; Sandel et al., 2015) and Fishbase (n = 1; Froese \& Pauly,
2016) were also included. When available, information on sampling
methods, gender differentiation, location, and depth ranges of each
study was retrieved. Whenever gender was not specified, it was assumed
that the results were presented for pooled genders.

During the review process, some papers indistinctly used \(a\) to report
either the ponderal index in eq. 1 or the y-intercept (\(c\)) in eq. 3,
which might sometimes be overlooked. Furthermore, some studies reported
their parameters as mm-to-gr conversions, but a rapid evaluation of such
parameters indicated that they were estimated as cm-to-gr conversions.
Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
required, values from other studies were transformed for consistency.

Since uncertainty arround estimated relationships was not reported in
some of the reviewed studies, it was not possible to test for
statistical differences between relationships. Instead, the 13
length-weight relationships were usd to calculate expected weight for
the organisms sampled in the Central Mexican Caribbean (n = 109).
Expected weights were divided by the observed weights to obtain a ratio.
Difference in mean weight ratios across studies were tested with a
one-way Analysis of Variance (ANOVA).

All hypothesis testing was performed with an \emph{a priori} confidence
level of \(\alpha = 0.01\) in R version 3.4.0 (R Core Team, 2017). Data
wrangling was done with the tidyverse package (Wickham, 2017). Maps were
created with a mix of functions from the sp (Pebesma \& Bivand, 2005),
rgdal (Bivand, Keitt \& Rowlingson, 2017), tmap (Tennekes, 2017a), and
tmaptools (Tennekes, 2017b) packages. Heteroskedastic-robust standard
errors were calculated with the sandwich (Zeileis, 2004) and lmtest
(Zeileis \& Hothorn, 2002) packages. Models were manipulated with the
broom package (Robinson, 2017). RefManageR (McLean, 2014) was used to
keep track of citations. Raw data and code used in this work is
available at \url{github.com/jcvdav/lionfish_biometry}.

\section{RESULTS}\label{results}

Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7
gr. The smallest organism (TL = 34.00 mm) was also the lightest organism
(TW = 0.30 gr). However, the largest organism (TL = 310.00 mm) was not
the heaviest (TW = 303.70 gr), and the heaviest organism (TW = 397.70
gr) was 292.00 mm in total length. Kernell density plots (Fig. 2) show
the distribution for TL and TW for all sampled organisms. Both measures
were positively skewed, with skewness of 0.87 for TL and 2.25 for TW.

\textbf{Length-weight relationship.} The model adjusted to eq. 3
estimated the coefficient values at \(b = 3.2347391\) and
\(c = -5.4940866\). Thus, TW (gr) can be calculated from TL (mm) as a
linear equation:
\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
The intercept (\(c\)) and slope \((b)\) were significantly different
from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
respectively), rejecting the null hypothesis of no change. Additionally,
the allometric factor (\(b\)) was significantly different from the value
of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)), indicating
that lionfish present allometric growth. More information on model fit
and confidence intervals for the estimated coefficients is presented in
Table 2. The relationship between Total Length and Total Weight is
presented in Figure 3.

\textbf{Comparison of allometric parameters.} From the eight
peer-reviewed studies including information on growth parameters for
\emph{P. volitans} and Fishbase (Froese \& Pauly, 2016), 13 parameters
were identified (Table 3). Two studies (Fogg et al., 2013;
Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and pooled
parameters, while the rest presented pooled results. The smallest
coefficient of determination was presented by Chin, Aiken \& Buddo
(2016) with \(R^2 = 0.8715\), while Sabido-Itza et al. (2016) reported
the highest value at \(R^2 = 0.9907\). Reviewed studies presented
information for organisms obtained at depths between 0.5 and 57 m. Two
studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo,
2016) explicitly stated that their organisms were sampled with pole
spears. Five studies (Barbour et al., 2011; Fogg et al., 2013; Edwards,
Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et al., 2016)
mentioned that some of their organisms were obtained with pole spears
(or other type of harpoon). A single study (de Leon et al., 2013) did
not specify how organisms were sampled.

Parameters from models fit to males or females exclusively tend to have
a higher steepness (\emph{i.e.} higher allometric parameter), with mean
\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
\(b = 3.31 \pm 0.23\) for males and females respectively, compared to
parameters from models for pooled genders with a mean \(\pm\) standard
deviation value of \(b = 3.09 \pm 0.22\). In the case of the ponderal
index (\(a\)) and its \(log_{10}\) transformed parameter (\(c\)), values
were higher for parameters for pooled genders. Figure 4 shows the
predicted weights for organisms within the size range of these study
using the 14 parameters previously described.

There were significant differences in expected-to-observed weight ratios
estimated for each pair of parameters (F(13, 1512) = 39.28; p
\textless{} 0.05). From all allometric parameters reviewed, those of
Edwards, Frazer \& Jacoby (2014) provided the lowest weight estimates,
with an expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean
\(\pm\) SD). On the other hand, Barbour et al. (2011) yielded the
highest weight estimates, with a mean (\(\pm\) SD) expected-to-observed
weight ratio of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios
and groups identified by Tukey's HSD (\(\alpha = 0.05\)) are presented
in Figure 5.

\section{DISCUSSION}\label{discussion}

This study provides the first pair of allometric growth parameters
specific to the Central Mexican Caribbean, complementing other studies
performed in Mexican waters in the Alacranes Reef (Aguilar-Perera \&
Quijano-Puerto, 2016) and Xcalak National Park (Sabido-Itza et al.,
2016). By using hand nets instead of spears, we are able to sample a
wider range of sizes often ignored by pole spear samples, allowing us to
include smaller organisms. Estimating parameters by including smaller
organisms ensures better estimation of weight for smaller sizes. This is
especially important when biomass is calculated from visual census,
where small organisms can be registered. Thus, this study also increases
certainty in weight estimation of small organisms.

The length-weight coefficients estimated in this study were within the
range identified by studies in other regions (Barbour et al., 2011; de
Leon et al., 2013; Fogg et al., 2013; Edwards, Frazer \& Jacoby, 2014;
Sandel et al., 2015; Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken
\& Buddo, 2016; Sabido-Itza et al., 2016). However, the ones presented
here provide lower weight estimates for a same length. Until about TL =
200 mm, there are no appreciable differences between the parameters for
organisms from the Mexican Caribbean and those for little Cayman
(Edwards, Frazer \& Jacoby, 2014) and Jamaica (Chin, Aiken \& Buddo,
2016). Yet, for larger organisms (TL \textgreater{} 270 mm) parameters
from Costa Rica (Sandel et al., 2015) and Bonaire (de Leon et al., 2013)
provide similar estimates to those from this study. Conversely, these
same studies tend to estimate higher weights ---as compared to the ones
reported here--- for smaller organisms, likely due to the lack of small
organisms in the samples used to estimate their parameters. When ever
possible, future works should consider the use of hand nets to obtain
the samples not only for studies on weight-at-length, but also diet,
behavior and life history, where length can be an important factor.

There are evident differences in weight-at-length between organisms from
the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
estimates with parameters from the Gulf of Mexico and North-Western
Atlantic (Barbour et al., 2011; Fogg et al., 2013; Aguilar-Perera \&
Quijano-Puerto, 2016; Sabido-Itza et al., 2016) tend to be higher than
those from the Caribbean (de Leon et al., 2013; Edwards, Frazer \&
Jacoby, 2014; Sandel et al., 2015; Chin, Aiken \& Buddo, 2016), except
for the ones from Xcalak National Park, Mexico (Sabido-Itza et al.,
2016). This indicates that there are differences between lionfish across
the invasion range. Similar regional variation exist for age-at-length
relationships of lionfish (Fogg et al., 2015). These differences can
have major implications in management, especially when estimating
biomass available for harvest or predicting effects on local ecosystems,
or evaluating the effectiveness of removal programs. Using site-specific
values provides a more accurate estimate of fish biomass. Future
research should try to use, to the extent possible, parameters
calculated for their region, or use different parameters to provide
upper and lower bounds in their results. At the same time, this
highlights the need for more basic research that furthers our
understanding of lionfish biology. To better manageme the invasion, we
must perform research that can describe biologically important
information of lionfish throughout its invasion range (Johnson \&
Swenarton, 2016).
